---
title: "CS112 Assignment 3, Fall 2020"
author: "Evgeniia Buzulukova"
date: "11/01/2020"
output:
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
# Don't change this part of the document
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, 
                      message=FALSE, fig.width=6, fig.align="center")
# load the necessary packages
# If you don't have the following packages installed,
# please install them first. But don't include the installation
# code here because every time you knit this document they'll 
# be reinstalled which is not necessary!
library(Matching)
#library(MatchIt)
library(cobalt)
library(knitr)
library(janitor)
library(tidyverse)
library(gridExtra)
# we need to set the seed of R's random number generator, 
# in order to produce comparable results 
set.seed(928)
```

# A few important notes

**Option 1 for submitting your assignment**: *This method is actually preferred. This is an RMarkdown document. Did you know you can open this document in RStudio, edit it by adding your answers and code, and then knit it to a pdf? To submit your answers to this assignment, simply knit this file as a pdf and submit it as a pdf on Forum. All of your code must be included in the resulting pdf file, i.e., don't set echo = FALSE in any of your code chunks. To learn more about RMarkdown, watch the videos from session 1 and session 2 of the CS112B optional class. [This](https://rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf) is also a cheat sheet for using Rmarkdown. If you have questions about RMarkdown, please post them on Perusall. Try knitting this document in your RStudio. You should be able to get a pdf file. At any step, you can try knitting the document and recreate a pdf. If you get error, you might have incomplete code.*

**Option 2 for submitting your assignment**: *If you are not comfortable with RMarkdown, you can also choose the Google Doc version of this assignment, make a copy of it and edit the Google doc (include your code, figures, results, and explanations) and at the end download your Google Doc as a pdf and submit the pdf file.*

**Note**: *Either way (if you use Rmd and knit as pdf OR if you use Google Doc and download as pdf) you should make sure you put your name on top of the document.*

**Note**: *The first time you run this document you may get error that some packages don't exist. If you don't have the packages listed on top of this document, install them first and you won't get those errors.*

**Note**: *If you work with others or get help from others on the assignment, please provide the names of your partners at the top of this document. Working together is fine, but all must do and understand their own work and have to mention the collaboration on top of this document.*

**Note**: *Don't change seed in the document. The function `set.seed()` has already been set at the beginning of this document to 928. Changing the see again to a different number will make your results not replicable.*


## QUESTION 1: Data Generating Example

The following code, creates a toy dataset with a treatment variable, $D$, an outcome variable, $Y$, and other variables $V_1$ to $V_4$. 

```{r}
n = 1000
## Generating a random data set here
#Syntax for the normal distribution here is rnorm(sample size, mean, SD)
V1 = rnorm(n, 45, 10)
#getting a binary variable
V2 = sample(c(1,0), 
             replace = TRUE, 
             size = n,
             prob = c(.4,.6))
V3 = rnorm(n, V1/10, 1)
V4 = rnorm(n, 0, 1)
D  = as.numeric(pnorm(rnorm(n, .01*V1 + .8*V2 + 0.3*V3 + V4, 1), .45 + .32 + .3*4.5, 1) > .5)
Y  = rnorm(n, .8*D - 0.45*V2 - .4*V3 + 2, .2)
# combining everything in a data frame
df = data.frame(V1, V2, V3, V4, D, Y)
```

#### STEP 1

From the variables $V_1$, $V_2$, $V_3$, and $V_4$, which one(s) are not confounding variable(s) (covariates that causes confounding)? Remember, a rule of thumb (although not a perfect rule) is that the variable is correlated with both the treatment variable and the outcome variable. Explain!

I think $V_1$ and $V_4$ are not confounders as they are not correlated with the outcome variable explicitly. It means that $V_2$ and $V_3$ were used directly in the creation of outcome variable, while $V_1$ and $V_4$ were not. However, all of these variables are correlated with treatment variable. But the definition of confounding variable suggests that the confounding variable must be correlated with both treatment and outcome variable, so $V_1$ and $V_4$ are not confounding in this case as they are correlated only to treatment variable.

#### STEP 2

Can you figure out the true treatment effect by looking at the data generating process above?

Yes, because we know that when treatment is 1 (so the unit is treated), the outcome variable is increased by 0.8 (on the contrary, when treatment is 0, it is not changed). Therefore, the true treatment effect is 0.8.

#### STEP 3

Plot the outcome variable against the treatment variable. Make sure you label your axes. Do you see a trend?

```{r}
# plot the scatter plot
plot(df$D, df$Y, main="Outcome and Treatment Relationship", 
   xlab="Treatment variable", ylab="Outcome variable")

```
The trend is clearly seen, if we the unit is treated it tends to have bigger outcome variable on average.

#### STEP 4

Are the variables $V_1$, $V_2$, $V_3$, and $V_4$ balanced across the treatment and control groups? You can use any R function from any package to check this (for instance, you can check the cobalt package). Make sure you check all variables. 

**Note**: *This is optional but you can use the `gridExtra` package and its `grid.arrange()` function to put all the 4 graphs in one 2 x 2 graph. Read more about the package and how to use it here: https://cran.r-project.org/web/packages/egg/vignettes/Ecosystem.html. Set `nrow = 2`.*

```{r}
# create balance subplots 
p1 = bal.plot(df, "V1", treat = df$D )
p2 = bal.plot(df, "V2", treat = df$D)
p3 = bal.plot(df, "V3", treat = df$D)
p4 = bal.plot(df, "V4", treat = df$D)

#put subplots into the grid format
grid.arrange(p1,p2,p3,p4)

#show balance table
bal.tab(D ~ V1 + V2 + V3 + V4, data=df)
```
No, they are not balanced across treated and control groups.

#### STEP 5

Write code that would simply calculate the Prima Facie treatment effect in the data above. What's the Prima Facie treatment effect? Note that the outcome variable is binary.

```{r}
#calculate prima facie effect
mean(df[df$D == 1, 'Y']) - mean(df[df$D == 0, 'Y'])
```


#### STEP 6

Explain why the Prima Facie effect is not the true average causal effect from Step 2.

We have imbalance across treatment and control group. It leads to the inability to do assumptions about treatment effect based on the difference of means of treated and control groups.  Prima Facie is a naive solution to find the treatment affect and it cannot work to find the true causal effect in the observational data, as there is no randomization.


#### STEP 7

We can use matching to create a better balance of the covariates. Use a propensity score model that includes all the variables $V_1$, $V_2$, $V_3$, and $V_4$.

```{r}
#create linear model for propensity score
lm.prop <- glm(D ~ V1 + V2 + V3 + V4, data=df, family="binomial")
X <- lm.prop$fitted.values
# Do the matching
matchout.prop <- Match(Y = df$Y, Tr=df$D, X=X)

```


#### STEP 8

Check the balance of the covariates. Do you see any improvements after matching?


```{r}
#check balance
mb.out <- MatchBalance(D ~ V1 + V2 + V3 + V4, data=df, match.out = matchout.prop, nboots=1000)

#show balance table
bal.tab(matchout.prop, D ~ V1 + V2 + V3 + V4, data=df)
```

Of course there are improvements, we can see that the adjusted differences after matching became much smaller for all the covariates. It means the matching was successful.

#### STEP 9

What is the treatment effect after matching? Is this surprising given your answer to Step 2. Is the treatment effect found in this Step closer to the treatment effect in Step 2 than the treatment effect before matching?

```{r}
# show the treatment effect after matching
matchout.prop$est[1,1]
```
The treatment effect after matching is about 0.93. It is closer to the true treatment effect than the prima facie effect because we used matching to find it. Matching can help us to estimate more robust treatment effect if it would lead to the increased balance in covariates.

## QUESTION 2: Daughters

Read Section 5 (which is only about 1 page long!) of Iacus, King, Porro (2011), Multivariate Matching Methods That Are Monotonic Imbalance Bounding, JASA, V 106, N. 493, available here: https://gking.harvard.edu/files/gking/files/cem_jasa.pdf. Don't worry about the "CEM" elements. Focus on the "daughters" case study.

Data for this case study is available in "daughters" below.

```{r}
# read the data
daughters = read.csv(url("http://bit.ly/daughters_data")) %>% 
  clean_names()
```

#### STEP 1

Before doing any matching, run a regression, with the outcome variable being `nowtot`, the treatment variable being `hasgirls`, and the independent vars mentioned below:
- dems,
- repubs,
- christian,
- age,
- srvlng,
- demvote

Show the regression specification. Use the regression to estimate a treatment effect and confidence interval. Check the balance of this not-matched data set using any method of your choice (balance tables, balance plots, love plots, etc).

```{r}
#create regression model
lm1 = lm(nowtot ~ hasgirls + dems + repubs + christian + age + srvlng + demvote, data = daughters)

#show summary of regression model
summary(lm1)

#show confidence intervals of coefficients
confint(lm1)

#show love plot before balance
love.plot(bal.tab(hasgirls ~ dems + repubs + christian + age + srvlng + demvote, data = daughters))
```


#### STEP 2

Then, do genetic matching. Use the same variables as in the regression above. Make sure to set `estimand = "ATT"`. What's your treatment effect?

**Note**: *For replicability purposes, we need to choose a see for the `GenMatch()` function. However, setting seed for `GenMatch()` is different. The usual practice of typing `set.seed(some number)` before the GenMatch line doesn't ensure stochastic stability. To set seeds for `GenMatch`, you have to run `GenMatch()` including instructions for genoud within `GenMatch()`, e.g.: `GenMatch(Tr, X, unif.seed = 123, int.seed = 92485...)`. You can find info on these `.seed elements` in the documentation for `genoud()`. The special .seed elements should only be present in the `GenMatch()` line, not elsewhere (because nothing besides `GenMatch()` runs genoud.*

**Note**: *When you use the `GenMatch()` function, wrap everything inside the following function `invisible(capture.output())`. This will reduce the unnecessary output produced from the GenMatch() function. For instance, you can say: `invisible(capture.output(genout_daughters <- GenMatch(...)))`*

```{r}
#create a table of covariates
X = cbind(daughters$dems,daughters$repubs,daughters$christian,daughters$age,daughters$srvlng,daughters$demvote)

# do the genetic matching while making output invisible
invisible(capture.output(genout_daughters <- GenMatch(Tr= daughters$hasgirls, X = X, unif.seed = 123, int.seed = 92485, estimand = 'ATT')))

#match using GenMatch weights matrix
matchout.gen <- Match(X = X, Tr = daughters$hasgirls, Y = daughters$nowtot, Weight.matrix=genout_daughters)

#show treatment effect after matching
matchout.gen$est

#check balance
mb.out3 <- MatchBalance(hasgirls ~ dems + repubs + christian + age + srvlng + demvote, data=daughters, match.out = matchout.gen, nboots=1000)

#create love plot after matching and before it
love.plot(bal.tab(matchout.gen, hasgirls ~ dems + repubs + christian + age + srvlng + demvote, data = daughters))
```


#### STEP 3

Summarize (in 5-15 sentences) the genetic matching procedure and results, including what you matched on, what you balanced on, and what your balance results were. Provide output for MatchBalance() in the body of your submission. 

Genetic matching iteratively check the weights for each covariate and finds the suboptimal solution of matching the units. Here, I matched based on several covariates such as dems, repubs, christian, age, srvlng and demvote. I used ATT which means average treatment for treated, it means that for every treated unit the match was found. If the not all controls are matched, they are discarded. As we can see from the love plot and MatchBalance function, for some of the covariates standard mean difference became 0 (repubs, christian), which means there is absolutely no imbalance between treatment and control groups based on this covariate. All other covariates are also much more balanced than before the matching. All of this means the matching was great in terms of providing balance on important covariates.

#### STEP 4

Is your treatment effect different from the one reported before matching? By how much? If your numbers are different, provide some explanation as to why the two numbers are different. If they're not, provide an explanation why they're not different.

The treatment effect is extremely different from the treatment coefficient from linear regression (which was even negative). It is reasonable as the data was extremely unbalanced (especially on age), so the prima facie treatment effect cannot be true causal effect. 
 
#### STEP 5

Change the parameters in your genetic matching algorithm to improve the balance of the covariates. Consider rerunning with M = 2 or 3 or more. Consider increasing other parameters in the `GenMatch()` function such as the number of generations and population size, caliper, etc. Try 10 different ways but don't report the results of the genetic matching weights or the balance in this document. Only report the treatment effect of your top 3 matches. For instance, run the `Match()` function three times for your top 3 genout objects. Make sure the summary reports the treatment effect estimate, the standard error, and the confidence interval. Do you see a large variation in your treatment effect between your top 3 models?

**Note**: *For replicability purposes, we need to choose a see for the `GenMatch()` function. However, setting seed for `GenMatch()` is different. The usual practice of typing `set.seed(123)` before the GenMatch line doesn't ensure stochastic stability. To set seeds for `GenMatch`, you have to run `GenMatch()` including instructions for genoud within `GenMatch()`, e.g.: `GenMatch(Tr, X, unif.seed = 123, int.seed = 92485...)`. You can find info on these `.seed elements` in the documentation for `genoud()`. The special .seed elements should only be present in the `GenMatch()` line, not elsewhere (because nothing besides `GenMatch()` runs genoud.*

**Note**: *When you use the `GenMatch()` function, wrap everything inside the following function `invisible(capture.output())`. This will reduce the unnecessary output produced with the GenMatch() function. For instance, you can say: `invisible(capture.output(genout_daughters <- GenMatch(...)))`*

**Note**: *In the matching assignment, you may find that the Genetic Matching step takes a while, e.g., hours. If you have to reduce pop.size to e.g., 10 or 16 to ensure it stops after only an hour or two, that's fine. Running your computer for an hour or two is a good thing. Running it for a full day or more is unnecessary overkill (and if this is your situation, change hyperparameters like pop.size to reduce run-time). For example, we suggest you modify the pop.size (e.g., you can set it to 5!), max.generations (set it to 2!), and wait.generations (set it to 1!) and that should expedite things.*

**Note**: *Can you set a caliper for one confounding variable, and not others (e.g., only set a caliper for "age")? No and yes. No, strictly speaking you can't. But yes, practically speaking you can, if you set other calipers (for the other confounders) that are so wide as to not induce any constraints. E.g., in GenMatch, and Match, you could set `caliper = c(1e16, 1e16, 0.5, 1e16)` and this would induce a certain meaningful caliper for the third confounder in X, without constraining the other confounders (because 1e16 implies a caliper that is so enormously wide that it does not, in practical terms, serve as a caliper at all).*

```{r}

invisible(capture.output(genout_daughters <- GenMatch(Tr= daughters$hasgirls, X = X, unif.seed = 123, int.seed = 92485, estimand = 'ATT', M = 2)))

matchout.gen <- Match(X = X, Tr = daughters$hasgirls, Y = daughters$nowtot, Weight.matrix=genout_daughters)

mb.out3 <- MatchBalance(hasgirls ~ dems + repubs + christian + age + srvlng + demvote, data=daughters, match.out = matchout.gen, nboots=1000)

love.plot(bal.tab(matchout.gen, hasgirls ~ dems + repubs + christian + age + srvlng + demvote, data = daughters))
matchout.gen$est
```
```{r}
invisible(capture.output(genout_daughters <- GenMatch(Tr= daughters$hasgirls, X = X, unif.seed = 123, int.seed = 92485, estimand = 'ATT', M = 3, max.generations = 1000)))

matchout.gen <- Match(X = X, Tr = daughters$hasgirls, Y = daughters$nowtot, Weight.matrix=genout_daughters)

mb.out3 <- MatchBalance(hasgirls ~ dems + repubs + christian + age + srvlng + demvote, data=daughters, match.out = matchout.gen, nboots=1000)

matchout.gen$est

love.plot(bal.tab(matchout.gen, hasgirls ~ dems + repubs + christian + age + srvlng + demvote, data = daughters))
```
```{r}
invisible(capture.output(genout_daughters <- GenMatch(Tr= daughters$hasgirls, X = X, unif.seed = 123, int.seed = 92485, estimand = 'ATT', M = 2, max.generations = 1000)))

matchout.gen <- Match(X = X, Tr = daughters$hasgirls, Y = daughters$nowtot, Weight.matrix=genout_daughters)

mb.out3 <- MatchBalance(hasgirls ~ dems + repubs + christian + age + srvlng + demvote, data=daughters, match.out = matchout.gen, nboots=1000)

matchout.gen$est

love.plot(bal.tab(matchout.gen, hasgirls ~ dems + repubs + christian + age + srvlng + demvote, data = daughters))
```
There is a significant variation in treatment effect.

#### STEP 6

Repeat everything you've done for Steps 1-2, including the regression, genetic algorithm, code and estimating the treatment effect EXCEPT this time change the definition of treatment to cover 2 girls or more, and change the definition of control to cover 2 boys or more. Exclude all observations that don't meet these requirements. Be sure to explain (in a sentence or two) what you're doing with your new treatment and control definitions. Do your new definitions change anything?

**Note**: *Definition of the new treatment variable is as follows: Individuals in the treatment group should be having 2 or more girls and no boys, and individuals in the control group should be having 2 or more boys and no girls. What I had in mind was that such a situation increased the "dosage" of treatment vs. the "dosage" of control (and Rosenbaum alluded to this kind of observational design logic in one of the recently assigned articles). Note that you can't have the same units in the treatment group AND the control group -- we should all know by now that such a situation would be wrong.*


```{r}
daughters <- daughters[((daughters$ngirls >= 2) & (daughters$nboys == 0)) | ((daughters$ngirls == 0) & (daughters$nboys >= 2)),]

lm1 = lm(nowtot ~ hasgirls + dems + repubs + christian + age + srvlng + demvote, data = daughters)

summary(lm1)

confint(lm1)

love.plot(bal.tab(hasgirls ~ dems + repubs + christian + age + srvlng + demvote, data = daughters))
```
```{r}
X = cbind(daughters$dems,daughters$repubs,daughters$christian,daughters$age,daughters$srvlng,daughters$demvote)

invisible(capture.output(genout_daughters <- GenMatch(Tr= daughters$hasgirls, X = X, unif.seed = 123, int.seed = 92485, estimand = 'ATT', max.generations = 1000)))

matchout.gen <- Match(X = X, Tr = daughters$hasgirls, Y = daughters$nowtot, Weight.matrix=genout_daughters)

mb.out3 <- MatchBalance(hasgirls ~ dems + repubs + christian + age + srvlng + demvote, data=daughters, match.out = matchout.gen, nboots=1000)

matchout.gen$est

love.plot(bal.tab(matchout.gen, hasgirls ~ dems + repubs + christian + age + srvlng + demvote, data = daughters))
```
New treatment as to have only girls as children and only more than 1 girl. The new control is to have only boys as children and only more than 1 boy. The results are very different as the treatment effect has grown tremendeously even though we did sufficient matching on the important covariates.

#### STEP 7

It is NOT wise to match or balance on "totchi". What is the reason? Hint: You will have to look at what variables mean in the data set to be able to answer this question.

totchi is the variable of total number of children. Here, it is not important as we know that a person has a children of only one gender: boy or girl, therefore, we do not really need to balance on the number of children because it makes no difference. The idea here is to look at how gender of the kid affects, rather than the number of kids.


## QUESTION 3: COPD

Most causal studies on the health effects of smoking are observational studies (well, for very obvious reasons). In this exercise, we are specifically after answer the following question: Does smoking increase the risk of chronic obstructive pulmonary disease (COPD)? To learn more about the disease, read here: https://www.cdc.gov/copd/index.html

We’ll use a sub-sample of the 2015 BRFSS survey (pronounced bur-fiss), which stands for Behavioral Risk Factor Surveillance System. The data is collected through a phone survey across American citizens regarding their health-related risk behaviors and chronic health conditions. Although, the entire survey has over 400,000 records and over 300 variables, we only sample 5,000 observations and 7 variables.

Let's load the data first and take a look at the first few rows:

```{r}
#read the data
brfss = read.csv("http://bit.ly/BRFSS_data") %>% 
  clean_names()
head(brfss)
```

A summary of the variables is as follows:

- copd: Ever told you have chronic obstructive pulmonary disease (COPD)?
- smoke: Adults who are current smokers (0 = no, 1 = yes)
- race: Race group
- age: age group
- sex: gender
- wtlbs: weight in pounds (lbs)
- avedrnk2: During the past 30 days, when you drank, how many drinks did you drink on average?

#### STEP 1

Check the balance of covariates before matching using any method of your choice. You can look at balance tables, balance plots, or love plots from any package of your choice. Do you see a balance across the covariates?

**Note**: *This is optional but you can use the `gridExtra` package and its `grid.arrange()` function to put all the 4 graphs in one 2 x 2 graph. Read more about the package and how to use it here: https://cran.r-project.org/web/packages/egg/vignettes/Ecosystem.html. Set `nrow = 2`.*

```{r}
#create subplots for each covariate
p1 = bal.plot(brfss, "race", treat = brfss$smoke )
p2 = bal.plot(brfss, "age", treat = brfss$smoke)
p3 = bal.plot(brfss, "sex", treat = brfss$smoke)
p4 = bal.plot(brfss, "wtlbs", treat = brfss$smoke)
p5 = bal.plot(brfss, "avedrnk2", treat = brfss$smoke)

#arrange plots in a grid
grid.arrange(p1,p2,p3,p4, p5)

#show love plot before balance
bal.tab(smoke ~ race + age + sex + wtlbs + avedrnk2, data=brfss)
```
There is some balance for some covariates, but not all of them are perfectly balanced, so it can require matching before doing any treatment effect estimations.

#### STEP 2

Now, let's do Mahalanobis distance matching. Note that you can use the same old `Match()` function. Use all covariates in the data set to match on, however, make sure you convert all categorical variables into factor variables (Google to see how). We are going to specify `estimand = "ATT"` in the `Match()` function. What's the treatment effect after matching?


```{r}
#create table of covariates
attach(brfss)
X <- cbind(race, age, sex, wtlbs, avedrnk2)
detach(brfss)

matchout <- Match(Y = brfss$copd, Tr=brfss$smoke, X=X, estimand = "ATT")
mb.out2 <- MatchBalance(smoke ~ race + age + sex + wtlbs + avedrnk2, data=brfss, match.out = matchout, nboots=1000)
bal.tab(matchout, smoke ~ race + age + sex + wtlbs + avedrnk2, data=brfss)
matchout$est
love.plot(bal.tab(matchout, smoke ~ race + age + sex + wtlbs + avedrnk2, data=brfss))

```


#### STEP 3

Provide a few sentences talking about the number of treated units dropped, and a few more sentences talking about the balance obtained. 

As we used ATT, no treated units was dropped, but 2650 control units were dropped. It is because we bring all treated units, find them a match, and drop all unmatched controls. The balance is increased for some covariates and decresed for some other covariates. It means that even though balance procedure worked well, it worsen some of the balanced initially covariates such as weight in lbs.


#### STEP 4

Now, let's do another Mahalanobis distance matching. Use all covariates in the data set in the propensity score estimation. However, this time make sure you specify `estimand = "ATE"` in the `Match()` function. What's the treatment effect after matching?

```{r}
matchout <- Match(Y = brfss$copd, Tr=brfss$smoke, X=X, estimand = "ATE")
mb.out2 <- MatchBalance(smoke ~ race + age + sex + wtlbs + avedrnk2, data=brfss, match.out = matchout, nboots=1000)
bal.tab(matchout, smoke ~ race + age + sex + wtlbs + avedrnk2, data=brfss)
matchout$est
love.plot(bal.tab(matchout, smoke ~ race + age + sex + wtlbs + avedrnk2, data=brfss))
```

#### STEP 5

Are your answers in Steps 2 and 4 different? Why? What does the matching process do differently in each step? Which answer do you trust more?

The answers are a bit different; however, not a lot. They are different because we used a little bit different technique to estimate the treatment effect. For ATT, we just calculated the treatment effect while matching treated units and dropping unused controls; while in ATE, we did this and also calculated the treatment effect while matching control units and dropping unused treated. Therefore, the ATE approach is more reliable as it use two methods and combines them in order to get unbiased answer.

## BONUS QUESTION: Sensitivity Analysis

#### STEP 1

Use the BRFSS data set from the previous question. Now, identify the critical value of Gamma as we discussed in the class. Do it using rbounds: https://nbviewer.jupyter.org/gist/viniciusmss/a156c3f22081fb5c690cdd58658f61fa

```{r}
library(rbounds)

psens(matchout, Gamma=4, GammaInc=.5)

```


#### STEP 2

Then, write a paragraph explaining what you found. Your paragraph should include numbers obtained from your analysis and explain what those numbers mean as simply as you can. 

The critical gamma is 2. When there is 2 times more (or more than 2 times more) chance for some unit to be treated than the other unit, the p-value of the treatment effect estimate becomes bigger and bigger which means the treatment effect is not reliable. As we can see, the data we use is not very stable to increase in gamma. Therefore, it is sensitive to hidden bias (unobserved confounders).


# End of Assignment

## Final Steps

Before finalizing your project you'll want be sure there are **comments in your code chunks** and **text outside of your code chunks** to explain what you're doing in each code chunk. These explanations are incredibly helpful for someone who doesn't code or someone unfamiliar to your project.

You have two options for submission:

1. You can complete this .rmd file, knit it to pdf and submit the resulting .pdf file on Forum.
2. You can complete the Google Doc version of this assignment, include your code, graphs, results, and your explanations wherever necessary and download the Google Doc as a pdf file and submit the pdf file on Forum. If you choose this method, you need to make sure you will provide a link to an .R script file where you code can be found (you can host your code on Github or Google Drive). Note that links to Google Docs are not accepted as your final submission.


### Knitting your R Markdown Document

Last but not least, you'll want to **Knit your .Rmd document into a pdf document**. If you get an error, take a look at what the error says and edit your .Rmd document. Then, try to Knit again! Troubleshooting these error messages will teach you a lot about coding in R. If you get any error that doesn't make sense to you, post it on Perusall.


Good Luck! The CS112 Teaching Team